Viscous Transport in Eroding Porous Media

### 2019-08-05 docs/transport/erosion_transport.tex
modify figure of transport paper

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian}
\caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
eroding geometry initialized with 20 bodies.  The tortuosity is
calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian approach of tortuosity. 
The blue dots are Eulerian approach of tortuosity and the red stars and 
square are Lagrangian approach of tortuosity. 
The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and 
the the sum $S$ of squared residuals is 0.0075.}
\end{figure}

>>>>

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian}
\caption{\label{fig:Eroding20tort_all} The tortuosity inside of an
eroding geometry initialized with 20 bodies.  The tortuosity is
calculated using the Eulerian method~\eqref{eqn:tortuosity2} (blue dots)
and Lagrangian method~\eqref{eqn:tortuosity1} (red stars).  The red
square correspond to the geometry in Figure~\ref{fig:Eroding20tort}(c).
The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2228$ and 
the sum $S$ of squared residuals is 0.0166.}
\end{figure}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian approach of tortuosity. 
The blue dots are Eulerian approach of tortuosity and the red stars and 
square are Lagrangian approach of tortuosity. 
The dash line is the fitting line $\hat{T}(\phi)=1-p\ln\phi$ as $p=0.2631$ and 
the sum $S$ of squared residuals is 0.0075.}
\end{figure}
